Optimization of E-Commerce Product Discount Portfolio Using Dynamic Spiral Optimization Algorithm

### 2022-04-11 Semester II/Research Method/Tugas Kuliah IV/draft.Rmd
update

In another study, researchers made an adaptive linear SDOA by changing the value of the contraction constant into a specific function that depends on the function value of each candidate solution [@sdoa2]. The latest study in 2022 conducted a thorough review, including making several improvements to SDOA, such as
- Changing the value of the contraction constant,
- Utilizing alternative functions (linear, quadratic, fuzzy, and exponential), and
- Crossing between SDOA and PSO into PSO with a spiral movement [@sdoa3].

>>>>

In another study, researchers made an adaptive linear SDOA by changing the value of the contraction constant into a specific function that depends on the function value of each candidate solution [@sdoa2]. The latest study in 2022 conducted a thorough review, including making several improvements to SDOA  [@sdoa3], such as:

- Changing the value of the contraction constant,
- Utilizing alternative functions (linear, quadratic, fuzzy, and exponential), and
- Crossing between SDOA and PSO into PSO with a spiral movement.
